### 2018-12-17 README.Rmd
update installation instructions

## Installation
### Installing Dependencies
You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package. Instructions vary significantly by operating system. For best results, have `sf` installed before you install `qualmap`. Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.

>>>>

## Installation
### Installing Dependencies
You should check the [`sf` package website](https://r-spatial.github.io/sf/) for the latest details on installing dependencies for that package. Instructions vary significantly by operating system. For best results, have `sf` installed before you install `areal`. Other dependencies, like `dplyr`, will be installed automatically with `areal` if they are not already present.

The one exception here is the dependency `lwgeom`, which Linux users will need to follow some [spatial instructions](https://github.com/r-spatial/lwgeom) to install correctly.
